---
title: "Guide for Slick Developers"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Developer's Guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo=FALSE
)
```

```{r setup}
library(Slick)
```

# Introduction

## Slick Presentation of MSE Results

MSEs have four axes over which results are generally presented: 

1. operating models (a state of nature or scenario for real system dynamics)  
2. management procedures (MP - a management option, aka. harvest strategy)
3. performance metrics (aka. cost function, utility measure)
4. Uncertainty within an operating model (multiple simulations for each discrete state of nature)

Slick allows users to filter operating models, performance metrics and management procedures in order to explore robustness and characterize performance. Importantly, Slick is MSE-platform agnostic. Provided MSE practitioners format their results in a compatible Slick object, these can be loaded to the App. 

Slick presents MSE results in 11 Figures designed to inform decision making by revealing the absolute and comparative performance of candidate management procedures 
