---
title: "Developer's Guide"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Slick)
```

# Introduction

This document is a guide for analysts who wish to use `Slick` to summarize their MSE results. It describes the format of the `Slick` object, and provides examples demonstrating how to create and populate a `Slick` object.


## Reporting Issues and Bugs

Please use the [Issues](https://github.com/Blue-Matter/Slick/issues) feature in the GitHub repository to report issues or bugs. Please be sure to include a reproducible example so the issue can be recreated for de-bugging. [Pull Requests](https://github.com/Blue-Matter/Slick/pulls) are also welcome.


# The `Slick` Object

To use `Slick`, MSE results must be compiled into a `Slick` class object. The `Slick` object contains all of the information shown in the plots and tables, as well as metadata information such as title, introduction, and author details. Help documentation for the `Slick` class object can be found [here](../reference/Slick-class.html).

To create a `Slick` object, simply use the `Slick()` function:

```{r}
slick <- Slick()
```

`slick` is now an empty `Slick` class object:

```{r}
slick
```



## Title, Author details, and Introduction

The Title, Subtitle, Author, Email, and Institution components of the `Slick` object are populated with the corresponding functions. These are optional, but useful when presenting the Slick results in the App:

```{r}
Title(slick) <- 'An Example Slick Object'
Subtitle(slick) <- "This is the subtitle"
Author(slick) <- 'Adrian Hordyk'
Email(slick) <-  "[adrian@bluematterscience.com](mailto:adrian@bluematterscience.com)"
Institution(slick) <- "[Blue Matter Science](bluematterscience.com)"
```

The same functions are used to return the information stored in each component:

```{r}
Title(slick)
Subtitle(slick) 
Author(slick) 
Email(slick)
Institution(slick)
```

With the exception of `Date`, Markdown can be used to include links, text styling, etc. For example,

```{r}
Introduction(slick) <- "
This is an example Slick object. It has been created for the purposes of demonstrating the key features of Slick.

The introduction can include paragraphs as well as Markdown such as *italics* and **bold** text and [Links](https://slick.bluematterscience.com).


"
```

The Markdown will be automatically converted to HTML in the App:

```{r}
Introduction(slick, markdown = TRUE) 
```


### Multi-language 

`Title`, `Subtitle`, and `Introduction` support multiple languages. Currently three languages are supported:

- `en`: English
- `es`: Spanish
- `fr`: French

Multiple languages can included by providing a named list:

```{r}
Title(slick) <- list(en='This is the English Title',
                     es='This is the Spanish Title',
                     fr='This is the French Title')

```

```{r}
Title(slick)
Title(slick, 'es')
Title(slick, 'fr')
```

# The `MPs` object

The [`MPs` object](../reference/MPs-methods.html) contains the codes, labels, and descriptions of the management procedures (MPs) included in the `Slick` object.

`Code`, and `Label` are required. 

In this example, there are four MPs:


```{r}
mps <- MPs()
Code(mps) <- c('MP1', 'MP2', 'MP3', 'MP4')
Label(mps) <- c('MP 1', 'MP 2', 'MP 3', 'MP 4')
Description(mps) <- c('MP 1 is an example', 
                 'MP 2 is another example',
                 'Another example',
                 'The final example')

```

This could have also been done as:
```{r}
mps <- MPs(Code=c('MP1', 
                  'MP2', 
                  'MP3', 
                  'MP4'),
           Label=c('MP 1',
                   'MP 2', 
                   'MP 3', 
                   'MP 4'),
           Description = c('MP 1 is an example', 
                           'MP 2 is another example',
                           'Another example',
                           'The final example'))

```

`Color` is used to set the colors of the MPs shown in the plots. If not specified, default colors will be used:

```{r}
Color(mps)
```

`Preset` is an optional named list, with numeric values indicating the MPs to be selected by the `Preset` buttons:

```{r}
Preset(mps) <- list('All'=1:4,
                    'Last 2'=3:4)
```

Add `mp` to the `slick` object

```{r}
MPs(slick) <- mps
```


# The `OMs` Object
The `OMs` object describes the structure of the operating models contained with the `Slick` object. All `Slick` objects must have a completed `OMs` object.

The easiest way to build a `Slick` object is to create and populate the sub-components and then add them to the `Slick` object.


Create an [`OMs` object](../reference/OMs-methods.html):

```{r oms}
oms <- OMs()
```

The `OMs` object contains two mandatory slots (`Factors` and `Design`) and one optional slot (`Preset`).

## Factors

`Factors` is a `data.frame` with column headings **Factor**, **Level**, and **Description**. It is used to describe the various factors, and levels within each factor, of the operating models included in the `Slick` object.

Here is a simple example of a `Slick` object that includes results from 6 OMs, spanning three levels on uncertainty in natural mortality (M) and two levels of steepness (h):

```{r}
Factors(oms) <- data.frame(Factor=c(rep('M',3), rep('h',2)),
                           Level=c(0.1,0.2,0.3,0.7,0.9),
                           Description=c('Natural Mortality = 0.1',
                                         'Natural Mortality = 0.2',
                                         'Natural Mortality = 0.3',
                                         'Steepness = 0.7',
                                         'Steepness = 0.9')
                           )

Factors(oms)
```

## Design 

The `Design` matrix is `nOM` rows and `nFactor` columns. The values in each column should either be numeric values indicating the levels for the corresponding factor, or the actual level values (i.e., `Factors$Level`) that correspond to each OM. The column names of `Design` must match the names of the factors (i.e, `Factors$Level`).

Here is the `Design` matrix corresponding with the `Factors` above:

```{r design}
Design(oms) <- data.frame(M=c(0.1, 0.1, 0.2, 0.2, 0.3,0.3),
                          h=rep(c(0.7, 0.9), 3)
)
Design(oms)
```

## Preset

`Preset` is optional. It is used to add buttons to the `Slick` [App](../reference/App.html) where users can rapidly select different sets of OMs.

For `OMs` objects, `Preset` is a multi-level list. Each element in first level lists must be named. The names are used to display the 'Preset' button in the App. 

The second level of each named list element must be a list length `nFactors`, which each element containing numeric values representing the levels within each factor that should be included under that preset.

For example:
```{r}
Preset(oms) <- list('Low h'=list(1:3, 1),
                    'High h'=list(1:3, 2))
```


The `OMs` object is now complete.

The `Check` function can be used to make sure there are no errors:

```{r}
Check(oms)
```

Once the `OMs` object is complete, it can be added to the `Slick` object:

```{r}
OMs(slick) <- oms
```


# Plotting Objects

At least one of the six plot objects must be included in a `Slick` object. 

## `Boxplot`

`Code`, `Label`, and `Value` are required. 
```{r boxplot}
boxplot <- Boxplot(Code=c('PI 1', 'PI 2', 'PI 3'),
                   Label=c('Perf. Ind. 1', 'Perf. Ind. 2', 'Perf. Ind. 3'),
                   Description=c('This is the description of PI 1',
                                 'This is the description of PI 2',
                                 'This is the description of PI 3'))
```

`Value` is a numeric array containing the values of the performance indicators included in the `Boxplot` object. `Value` must have dimensions `c(nsim, nOM, nMP, nPI)`.

```{r}

Value(boxplot) <- array(runif(1E4), dim=c(50, 6, 4, 3))

```


```{r}
Boxplot(slick) <- boxplot
```

### Checking and Testing

The `Slick` object is now complete with the minimum requirements:

1. A complete `MPs` object
1. A complete `OMs` object
1. and at least one complete plotting object (`Boxplot` in this case)

The `Slick` object can be checked for completeness with the `Check` function:

```{}
Check(slick)
```

The `App` function can be used to run the app locally. Passing a `Slick` object as a named argument loads the object directly into the App:

```{r, eval=FALSE}
App(slick=slick)
```

## `Kobe` 

## `Quilt`


## `Spider`

## `Timeseries`


## `Tradeoff`





